---
title: "Collecting 5'UTRs of orthologous genes from budding yeasts"
author: "Edward Wallace"
date: "10th August 2019, updated 10th October"
output: html_document
---

# Summary 

This code retrieves 5'UTRs of orthologous genes in budding yeasts, using Ortholog groups in budding yeast from the 332 genomes paper: Tempo and Mode of Genome Evolution in the Budding Yeast Subphylum, https://doi.org/10.1016/j.cell.2018.10.023 

It is focused on 5'UTRs for post-WGD yeasts, and for genes that are bound by Ssd1 in **Saccharomyces cerevisiae**.

# Warnings

- These scripts won't run until data from [the figshare repository 5854692](https://figshare.com/articles/Tempo_and_mode_of_genome_evolution_in_the_budding_yeast_subphylum/5854692) is downloaded to the path `../data/figshare_5854692/`.
- The figshare repository lacks sequence data for some model organisms such as *Saccharomyces cerevisiae*, despite containing identically-formatted and thus commensurate data from almost every other species reported in the paper.
- The figshare repository does not contain readme files for all of its data so some conjecture has been used by EW.
- The ortholog groups are computed automatically and so need to be treated sceptically. For example, Ssd1/YDR293C has entirely unrelated membrane proteins in the same ortholog group. By contrast, Tos6/YNL300W's ortholog group extends only to *Saccharomyces*, omitting orthologs shown on [YGOB](http://ygob.ucd.ie/) such as *Candida glabrata* CAGL0M03773g. Hsp150/YJL159W orthologs from *Kazachstania* are likewise missing.
- Ortho group names were collected together from different files in the repo by EW, using code in `GetSsd1OrthologGroup.Rmd`, results in `../data_processed/allids_genes_343taxa.txt.zip`. this might have included errors, and also the starting data omits standard (e.g. genbank/entrez/uniprot) names for very many of them.
- UTR lengths used here are approximate; in fact there are no available UTR annotations for almost any fungal species, especially not the newer ones whose genomes may be reported for the first time in this paper.
- The code overall takes a couple of minutes to run on a laptop, and needs plenty of memory; `seq_ids_index` is a 350MB text file

# Code

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("OrthoGroupScripts.R")
```

```{r load_seq_ids_index}
# setwd("~/Repos/UTREvolutionYeasts/src/")
seq_ids_index <- read_tsv("../data_processed/allids_genes_343taxa.txt.zip",
                          comment="#",
                          col_names = c("species_plus_id",
                                        "species", 
                                        "s_id", 
                                        "gene_id", 
                                        "ortho_id", 
                                        "ortho_group"))
```

```{r load_Saccharomyces_gtf_fasta,dependson="load_seq_ids_index"}
Saccharomyces_spp <- c("Saccharomyces_cerevisiae",
                       "Saccharomyces_paradoxus",
                       "Saccharomyces_mikatae",
                       "Saccharomyces_kudriavzevii",
                       "Saccharomyces_arboricola",
                       "Saccharomyces_uvarum",
                       "Saccharomyces_eubayanus")

Saccharomyces_noncer <- Saccharomyces_spp[-1]

# Species in the Nakaseomyces genus
Nakaseomyces <- c("Nakaseomyces_nivariensis",
                       "Nakaseomyces_delphensis",
                       "Nakaseomyces_bracarensis",
                       "Candida_glabrata",
                       "Nakaseomyces_bacillisporus",
                       "Nakaseomyces_castellii")

# Species in the Kazachstania genus
Kazachstania <- .species_concordance %>% 
    filter(str_detect(species_id,"Kazachstan")) %>% 
    .$species_id

# Species in the Tetrapisispora genus
Tetrapisispora <- .species_concordance %>% 
    filter(str_detect(species_id,"Tetrapis") | 
             str_detect(species_id,"Vanderwalt")  |
             str_detect(species_id,"Yueomyces")) %>% 
    .$species_id

# Species in the Naumovozyma genus
Naumovozyma <- .species_concordance %>% 
    filter(str_detect(species_id,"Naumovozyma")) %>% 
    .$species_id


# These lines assemble lists of gtfs (features) separated by species
Nakaseomyces_gtf <- get_gtflist(Nakaseomyces)
Sacc_noncer_gtf  <- get_gtflist(Saccharomyces_noncer)
Kazachstania_gtf  <- get_gtflist(Kazachstania)
Tetrapisispora_gtf  <- get_gtflist(Tetrapisispora)

# These lines assemble lists of fastas (sequences) separated by species
Nakaseomyces_fasta <- get_fastalist(Nakaseomyces)
Sacc_noncer_fasta  <- get_fastalist(Saccharomyces_noncer)
Kazachstania_fasta <- get_fastalist(Kazachstania)
Tetrapisispora_fasta <- get_fastalist(Tetrapisispora)

```

### Tests

```{r test_get_seqs,dependson=c("load_Sacc_gtf_fasta","get_5UTRish")}
# This line tests that get_ortho_group works, for Pgk1.
Pgk1_Sacmore <- get_ortho_group("YAL038W",
                                species_list = c(Saccharomyces_spp,
                                                 Nakaseomyces)
                                )
get_one_upstream_seq(seq_id_line=Pgk1_Sacmore %>% 
                         filter(species=="Candida_glabrata") %>%
                         head(n=1),
                     fastalist=Nakaseomyces_fasta,
                     gtflist=Nakaseomyces_gtf) 

get_one_upstream_seq(seq_id_line=Pgk1_Sacmore %>% 
                         filter(species=="Nakaseomyces_delphensis") %>%
                         head(n=1),
                     fastalist=Nakaseomyces_fasta,
                     gtflist=Nakaseomyces_gtf)

Pgk1_Naka_seqs <- get_upstream_seqs(Pgk1_Sacmore %>% 
                         filter(species %in% Nakaseomyces),
                     fastalist=Nakaseomyces_fasta,
                     gtflist=Nakaseomyces_gtf)

Pgk1_Sacc_seqs <- get_upstream_seqs(Pgk1_Sacmore %>% 
                         filter(species %in% Saccharomyces_noncer),
                     fastalist=Sacc_noncer_fasta,
                     gtflist=Sacc_noncer_gtf)

```

# Obtain UTR seqs of ortholog groups

```{r get_TOS6_5UTRs,dependson=c("load_Sacc_gtf_fasta","get_5UTRish")}
# Tos6_Sacspp <- get_ortho_group("YNL300W",species_list = Saccharomyces_spp)
# Tos6_Sacc_200u <- 
#     get_upstream_seqs(Tos6_Sacspp %>% 
#                           filter(species %in% Saccharomyces_noncer),
#                       fastalist=Sacc_noncer_fasta,
#                       gtflist=Sacc_noncer_gtf,
#                       upstream=200,downstream=0)
# writeXStringSet(Tos6_Sacc_200u,"../results/ortho_UTR_groups/Sacc_noncer/Tos6_Saccharomyces_200upstream.fa")

Tos6_Sacc_200upseqs <- 
    get_ortho_upseqs("YNL300W",
                     species_list = Saccharomyces_noncer,                      
                     fastalist=Sacc_noncer_fasta,
                     gtflist=Sacc_noncer_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Tos6_Saccharomyces_200upstream.fa")

# Tos6 does not have annotated orthologs in Nakaseomyces
# Tos6_Naka_200upseqs <- 
#     get_ortho_upseqs("YNL300W",
#                      species_list = Nakaseomyces,                      
#                      fastalist=Nakaseomyces_fasta,
#                      gtflist=Nakaseomyces_gtf,
#                      upstream=200,downstream=0,
#                      fname_out="../results/ortho_UTR_groups/Sacc_noncer/Tos6_Nakaseomyces_200upstream.fa")

Tos1_Sacc_200upseqs <- 
    get_ortho_upseqs("YBR162C",
                     species_list = Saccharomyces_noncer,                      
                     fastalist=Sacc_noncer_fasta,
                     gtflist=Sacc_noncer_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Tos1_Saccharomyces_200upstream.fa")

Tos1_Naka_200upseqs <- 
    get_ortho_upseqs("YBR162C",
                     species_list = Nakaseomyces,                      
                     fastalist=Nakaseomyces_fasta,
                     gtflist=Nakaseomyces_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Tos1_Nakaseomyces_200upstream.fa")

Cts1_Sacc_200upseqs <- 
    get_ortho_upseqs("YLR286C",
                     species_list = Saccharomyces_noncer,                      
                     fastalist=Sacc_noncer_fasta,
                     gtflist=Sacc_noncer_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Cts1_Saccharomyces_200upstream.fa")

Cts1_Naka_200upseqs <- 
    get_ortho_upseqs("YLR286C",
                     species_list = Nakaseomyces,                      
                     fastalist=Nakaseomyces_fasta,
                     gtflist=Nakaseomyces_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Cts1_Nakaseomyces_200upstream.fa")


Sun4Sim1_Sacc_500upseqs <- 
    get_ortho_upseqs("YNL066W",
                     species_list = Saccharomyces_noncer,                      
                     fastalist=Sacc_noncer_fasta,
                     gtflist=Sacc_noncer_gtf,
                     upstream=500,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Sun4Sim1_Saccharomyces_500upstream.fa")

Sun4Sim1_Sacc_700upseqs <- 
    get_ortho_upseqs("YNL066W",
                     species_list = Saccharomyces_noncer,                      
                     fastalist=Sacc_noncer_fasta,
                     gtflist=Sacc_noncer_gtf,
                     upstream=700,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Sun4Sim1_Saccharomyces_700upstream.fa")

Sun4Sim1_Naka_700upseqs <- 
    get_ortho_upseqs("YNL066W",
                     species_list = Nakaseomyces,                      
                     fastalist=Nakaseomyces_fasta,
                     gtflist=Nakaseomyces_gtf,
                     upstream=700,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Sun4Sim1_Nakaseomyces_700upstream.fa")

Uth1Nca3_Sacc_200upseqs <- 
    get_ortho_upseqs("YKR042W",
                     species_list = Saccharomyces_noncer,                      
                     fastalist=Sacc_noncer_fasta,
                     gtflist=Sacc_noncer_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Uth1Nca3_Saccharomyces_200upstream.fa")

Uth1Nca3_Naka_200upseqs <-
    get_ortho_upseqs("YKR042W",
                     species_list = Nakaseomyces,
                     fastalist=Nakaseomyces_fasta,
                     gtflist=Nakaseomyces_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Uth1Nca3_Nakaseomyces_200upstream.fa")

Ccw12Ccw22_Sacc_200upseqs <-
    get_ortho_upseqs("YLR110C",
                     species_list = Saccharomyces_noncer,                      
                     fastalist=Sacc_noncer_fasta,
                     gtflist=Sacc_noncer_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Ccw12Ccw22_Saccharomyces_200upstream.fa")

Ccw12Ccw22_Naka_200upseqs <-
    get_ortho_upseqs("YLR110C",
                     species_list = Nakaseomyces,
                     fastalist=Nakaseomyces_fasta,
                     gtflist=Nakaseomyces_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Ccw12Ccw22_Nakaseomyces_200upstream.fa")

Dse2_Sacc_200upseqs <-
    get_ortho_upseqs("YHR143W",
                     species_list = Saccharomyces_noncer,                      
                     fastalist=Sacc_noncer_fasta,
                     gtflist=Sacc_noncer_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Dse2_Saccharomyces_200upstream.fa")

# Dse2_Naka_200upseqs <-
#     get_ortho_upseqs("YHR143W",
#                      species_list = Nakaseomyces,
#                      fastalist=Nakaseomyces_fasta,
#                      gtflist=Nakaseomyces_gtf,
#                      upstream=200,downstream=0,
#                      fname_out="../results/ortho_UTR_groups/Sacc_noncer/Dse2_Nakaseomyces_200upstream.fa")

Scw4Scw10_Sacc_200upseqs <-
    get_ortho_upseqs("YGR279C",
                     species_list = Saccharomyces_noncer,                      
                     fastalist=Sacc_noncer_fasta,
                     gtflist=Sacc_noncer_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Scw4Scw10_Saccharomyces_200upstream.fa")

Scw4Scw10_Naka_200upseqs <-
    get_ortho_upseqs("YGR279C",
                     species_list = Nakaseomyces,
                     fastalist=Nakaseomyces_fasta,
                     gtflist=Nakaseomyces_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Scw4Scw10_Nakaseomyces_200upstream.fa")

Lre1Hlr1_Sacc_200upseqs <-
    get_ortho_upseqs("YDR528W",
                     species_list = Saccharomyces_noncer,                      
                     fastalist=Sacc_noncer_fasta,
                     gtflist=Sacc_noncer_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Lre1Hlr1_Saccharomyces_200upstream.fa")

# Lre1Hlr1_Naka_200upseqs <-
#     get_ortho_upseqs("YDR528W",
#                      species_list = Nakaseomyces,
#                      fastalist=Nakaseomyces_fasta,
#                      gtflist=Nakaseomyces_gtf,
#                      upstream=200,downstream=0,
#                      fname_out="../results/ortho_UTR_groups/Sacc_noncer/Lre1Hlr1_Nakaseomyces_200upstream.fa")

Cln2Cln1_Sacc_200upseqs <-
    get_ortho_upseqs("YPL256C",
                     species_list = Saccharomyces_noncer,                      
                     fastalist=Sacc_noncer_fasta,
                     gtflist=Sacc_noncer_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Cln2Cln1_Saccharomyces_200upstream.fa")

Cln2Cln1_Naka_200upseqs <-
    get_ortho_upseqs("YPL256C",
                     species_list = Nakaseomyces,
                     fastalist=Nakaseomyces_fasta,
                     gtflist=Nakaseomyces_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Cln2Cln1_Nakaseomyces_200upstream.fa")

Ssd1_Sacc_500upseqs <-
    get_ortho_upseqs("YDR293C",
                     species_list = Saccharomyces_noncer,                      
                     fastalist=Sacc_noncer_fasta,
                     gtflist=Sacc_noncer_gtf,
                     upstream=500,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Ssd1_Saccharomyces_500upstream.fa")

Ssd1_Naka_500upseqs <-
    get_ortho_upseqs("YDR293C",
                     species_list = Nakaseomyces,
                     fastalist=Nakaseomyces_fasta,
                     gtflist=Nakaseomyces_gtf,
                     upstream=500,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Ssd1_Nakaseomyces_500upstream.fa")
```

```{r get_Kaza_5UTRs,dependson=c("load_Sacc_gtf_fasta","get_5UTRish")}

# Tos6 does not have annotated orthologs in Nakaseomyces
Tos6_Kaza_200upseqs <- 
    get_ortho_upseqs("YNL300W",
                     species_list = Kazachstania,                      
                     fastalist=Kazachstania_fasta,
                     gtflist=Kazachstania_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Tos6_Kazachstania_200upstream.fa")

Tos1_Kaza_200upseqs <- 
    get_ortho_upseqs("YBR162C",
                     species_list = Kazachstania,                      
                     fastalist=Kazachstania_fasta,
                     gtflist=Kazachstania_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Tos1_Kazachstania_200upstream.fa")

Cts1_Kaza_200upseqs <- 
    get_ortho_upseqs("YLR286C",
                     species_list = Kazachstania,                      
                     fastalist=Kazachstania_fasta,
                     gtflist=Kazachstania_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Cts1_Kazachstania_200upstream.fa")


Sun4Sim1_Kaza_700upseqs <- 
    get_ortho_upseqs("YNL066W",
                     species_list = Kazachstania,                      
                     fastalist=Kazachstania_fasta,
                     gtflist=Kazachstania_gtf,
                     upstream=700,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Sun4Sim1_Kazachstania_700upstream.fa")


Uth1Nca3_Kaza_200upseqs <-
    get_ortho_upseqs("YKR042W",
                     species_list = Kazachstania,
                     fastalist=Kazachstania_fasta,
                     gtflist=Kazachstania_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Uth1Nca3_Kazachstania_200upstream.fa")


Ccw12Ccw22_Kaza_200upseqs <-
    get_ortho_upseqs("YLR110C",
                     species_list = Kazachstania,
                     fastalist=Kazachstania_fasta,
                     gtflist=Kazachstania_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Ccw12Ccw22_Kazachstania_200upstream.fa")

# Dse2_Kaza_200upseqs <-
#     get_ortho_upseqs("YHR143W",
#                      species_list = Kazachstania,
#                      fastalist=Kazachstania_fasta,
#                      gtflist=Kazachstania_gtf,
#                      upstream=200,downstream=0,
#                      fname_out="../results/ortho_UTR_groups/Sacc_noncer/Dse2_Kazachstania_200upstream.fa")

Scw4Scw10_Kaza_200upseqs <-
    get_ortho_upseqs("YGR279C",
                     species_list = Kazachstania,
                     fastalist=Kazachstania_fasta,
                     gtflist=Kazachstania_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Scw4Scw10_Kazachstania_200upstream.fa")

# Lre1Hlr1_Kaza_200upseqs <-
#     get_ortho_upseqs("YDR528W",
#                      species_list = Kazachstania,
#                      fastalist=Kazachstania_fasta,
#                      gtflist=Kazachstania_gtf,
#                      upstream=200,downstream=0,
#                      fname_out="../results/ortho_UTR_groups/Sacc_noncer/Lre1Hlr1_Kazachstania_200upstream.fa")

Cln2Cln1_Kaza_200upseqs <-
    get_ortho_upseqs("YPL256C",
                     species_list = Kazachstania,
                     fastalist=Kazachstania_fasta,
                     gtflist=Kazachstania_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Cln2Cln1_Kazachstania_200upstream.fa")

Ssd1_Kaza_500upseqs <-
    get_ortho_upseqs("YDR293C",
                     species_list = Kazachstania,
                     fastalist=Kazachstania_fasta,
                     gtflist=Kazachstania_gtf,
                     upstream=500,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Ssd1_Kazachstania_500upstream.fa")
```

```{r get_Tetrapisispora_5UTRs,dependson=c("load_Sacc_gtf_fasta","get_5UTRish")}

# Tos6 does not have annotated orthologs in Tetrapisispora
# Tos6_Tetrapisispora_200upseqs <- 
#     get_ortho_upseqs("YNL300W",
#                      species_list = Tetrapisispora,                      
#                      fastalist=Tetrapisispora_fasta,
#                      gtflist=Tetrapisispora_gtf,
#                      upstream=200,downstream=0,
#                      fname_out="../results/ortho_UTR_groups/Sacc_noncer/Tos6_Tetrapisispora_200upstream.fa")

Tos1_Tetrapisispora_200upseqs <- 
    get_ortho_upseqs("YBR162C",
                     species_list = Tetrapisispora,                      
                     fastalist=Tetrapisispora_fasta,
                     gtflist=Tetrapisispora_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Tos1_Tetrapisispora_200upstream.fa")

Cts1_Tetrapisispora_200upseqs <- 
    get_ortho_upseqs("YLR286C",
                     species_list = Tetrapisispora,                      
                     fastalist=Tetrapisispora_fasta,
                     gtflist=Tetrapisispora_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Cts1_Tetrapisispora_200upstream.fa")


Sun4Sim1_Tetrapisispora_700upseqs <- 
    get_ortho_upseqs("YNL066W",
                     species_list = Tetrapisispora,                      
                     fastalist=Tetrapisispora_fasta,
                     gtflist=Tetrapisispora_gtf,
                     upstream=700,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Sun4Sim1_Tetrapisispora_700upstream.fa")


Uth1Nca3_Tetrapisispora_200upseqs <-
    get_ortho_upseqs("YKR042W",
                     species_list = Tetrapisispora,
                     fastalist=Tetrapisispora_fasta,
                     gtflist=Tetrapisispora_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Uth1Nca3_Tetrapisispora_200upstream.fa")


Ccw12Ccw22_Tetrapisispora_200upseqs <-
    get_ortho_upseqs("YLR110C",
                     species_list = Tetrapisispora,
                     fastalist=Tetrapisispora_fasta,
                     gtflist=Tetrapisispora_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Ccw12Ccw22_Tetrapisispora_200upstream.fa")

# Dse2_Tetrapisispora_200upseqs <-
#     get_ortho_upseqs("YHR143W",
#                      species_list = Tetrapisispora,
#                      fastalist=Tetrapisispora_fasta,
#                      gtflist=Tetrapisispora_gtf,
#                      upstream=200,downstream=0,
#                      fname_out="../results/ortho_UTR_groups/Sacc_noncer/Dse2_Tetrapisispora_200upstream.fa")

Scw4Scw10_Tetrapisispora_200upseqs <-
    get_ortho_upseqs("YGR279C",
                     species_list = Tetrapisispora,
                     fastalist=Tetrapisispora_fasta,
                     gtflist=Tetrapisispora_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Scw4Scw10_Tetrapisispora_200upstream.fa")

# Lre1Hlr1_Tetrapisispora_200upseqs <-
#     get_ortho_upseqs("YDR528W",
#                      species_list = Tetrapisispora,
#                      fastalist=Tetrapisispora_fasta,
#                      gtflist=Tetrapisispora_gtf,
#                      upstream=200,downstream=0,
#                      fname_out="../results/ortho_UTR_groups/Sacc_noncer/Lre1Hlr1_Tetrapisispora_200upstream.fa")

Cln2Cln1_Tetrapisispora_200upseqs <-
    get_ortho_upseqs("YPL256C",
                     species_list = Tetrapisispora,
                     fastalist=Tetrapisispora_fasta,
                     gtflist=Tetrapisispora_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Cln2Cln1_Tetrapisispora_200upstream.fa")

Ssd1_Tetrapisispora_500upseqs <-
    get_ortho_upseqs("YDR293C",
                     species_list = Tetrapisispora,
                     fastalist=Tetrapisispora_fasta,
                     gtflist=Tetrapisispora_gtf,
                     upstream=500,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Ssd1_Tetrapisispora_500upstream.fa")
```

```{r Hsp26_5UTRs}
Hsp26_Sacc_200upseqs <- 
    get_ortho_upseqs("YBR072W",
                     species_list = Saccharomyces_noncer,                      
                     fastalist=Sacc_noncer_fasta,
                     gtflist=Sacc_noncer_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Hsp26_Saccharomyces_200upstream.fa")

Hsp26_Naka_200upseqs <- 
    get_ortho_upseqs("YBR072W",
                     species_list = Nakaseomyces,                      
                     fastalist=Nakaseomyces_fasta,
                     gtflist=Nakaseomyces_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Hsp26_Nakaseomyces_200upstream.fa")

Hsp26_Kaza_200upseqs <- 
    get_ortho_upseqs("YBR072W",
                     species_list = Kazachstania,                      
                     fastalist=Kazachstania_fasta,
                     gtflist=Kazachstania_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Hsp26_Kazachstania_200upstream.fa")

```

```{r Hsp150_5UTRs}
Hsp150_Sacc_200upseqs <- 
    get_ortho_upseqs("YJL159W",
                     species_list = Saccharomyces_noncer,                      
                     fastalist=Sacc_noncer_fasta,
                     gtflist=Sacc_noncer_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Hsp150_Saccharomyces_200upstream.fa")

Hsp150_Naka_200upseqs <- 
    get_ortho_upseqs("YJL159W",
                     species_list = Nakaseomyces,                      
                     fastalist=Nakaseomyces_fasta,
                     gtflist=Nakaseomyces_gtf,
                     upstream=200,downstream=0,
                     fname_out="../results/ortho_UTR_groups/Sacc_noncer/Hsp150_Nakaseomyces_200upstream.fa")

# Hsp150_Kaza_200upseqs <- 
#     get_ortho_upseqs("YJL159W",
#                      species_list = Kazachstania,                      
#                      fastalist=Kazachstania_fasta,
#                      gtflist=Kazachstania_gtf,
#                      upstream=200,downstream=0,
#                      fname_out="../results/ortho_UTR_groups/Sacc_noncer/Hsp150_Kazachstania_200upstream.fa")
```

